---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---
## Kaggle HR ANalytics: Microsoft R Server Training

```{r}
library(dplyr)
library(purrr)
library(tidyr)
library(Hmisc)
```
```{r}
df <- read.csv("HR_comma_sep.csv")

df %>%
  summary

summary(df)
```

```{r}
df %>% 
  describe

summary(df)
```

```{r}
df %>% 
  glimpse
```

  
```{r}
df %>%
  group_by(salary) %>% 
  mutate(salary_low = (salary == "low")) %>%
  summarise(num_promotions = sum(promotion_last_5years),
            sum_people_exited = sum(left))
  
```
```{r}

df %>%
  group_by(salary) %>% 
  mutate(salary_low = (salary == "low")) %>%
  summarise(num_people = n(),
            frac_promotions = sum(promotion_last_5years)/num_people,
            frac_people_exited = sum(left)/num_people)
  
```
```{r}

df %>%
  group_by(salary) %>% 
  mutate(salary_low = (salary == "low")) %>%
  summarise(num_people = n(),
            frac_promotions = sum(promotion_last_5years)/num_people,
            frac_people_exited = sum(left)/num_people) -> df2
df2
  
```
#### Lab 1 - dplyr group by and summarise
- Taking 'df' as the start which is just our dataset:
  1. Group by the people who have and haven't left their firm
    - first step
  1.  What are the total no of people in each group?
    - summarse step
  1. How many had work accidents? 
    - summarise step
  1. How many had a positive review?
    - mutate a  boolean where true for a last evaluation above 50%
    - summarise of the sum() of that variabe
  1. What is the average satisfaction level?
    - averge is the mean() funtion

#My Solution
```{r}
df %>% 
  group_by(left) %>% 
  mutate(positive_review = (last_evaluation > .5 )) %>% 
  summarise(num_people_left = n(),
            Num_positive_review = sum(positive_review),
            num_accidents = sum(Work_accident),
            avg_satisfaction = mean(satisfaction_level)
            )
```
## Quick Tips for checking data
1. df$
1. df$Work_accident %>%  describe
1. df$Work_accident %>%  unique()
1. df %>%  sample_n(10)
1. ungroup